---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**(Work-In-Progress)**

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 8
)
```

# Load the Package and Fit a Path Model

```{r setup}
library(semdplot)
```

```{r}
# A sample dataset from semdplot
dat <- data_pa

library(lavaan)
mod <-
"
m11 ~ a11*x1 + a21*x2 + c1 + c2
m12 ~ b12*m11 + c1 + c2
m21 ~ a12*x1 + a22*x2 + c1 + c2
m22 ~ b22*m21 + c1 + c2
y1 ~ b12y1*m12 + c1 + c2
y2 ~ b22y2*m22 + c1 + c2
ind_1 := a11*b12*b12y1
ind_2 := a21*b22*b22y2
"
fit <- sem(mod, dat)
summary(fit, fit.measures = TRUE)
```

# Compute Residuals for the PLots

The function `casewise_residuals()` can be used to
compute the necessary residuals (please refer to
`vignettes("casewise_residuals")` on the computation):

```{r}
fit_res <- casewise_residuals(fit)
```

# Plot Partial Plots and Residual Plots for Selected Variables

The output of `casewise_residuals()` has a `plot()` method.
Simply use `plot()` can produce the plots. If necessary,
users can use `x_names` and `y_names` to set the $x$
and $y$ variables to be included:

```{r}
p <- plot(fit_res,
          x_names = c("x1", "x2", "m11", "m12", "m21"),
          y_names = c("m11", "m12", "m21", "m22", "y1", "y2"))
plot(p)
```

The output is a `ggplot2` plot. It can be customized.
Please refer to `plot.semdplot_residuals()` on the options.

# If A Path Does Not Exist, Add It

For paths not in the model but could have been added, residuals
can be computed by fitting a model with this path added.
This is done when calling `casewise_residuals()` and set
`add_path` to `TRUE:

```{r}
fit_res_add <- casewise_residuals(fit, add_path = TRUE)
```

If these residuals are computed, they will be plotted by
`plot.semdplot_residuals()`:

```{r}
p2 <- plot(fit_res_add,
           x_names = c("x1", "x2", "m11", "m12", "m21"),
           y_names = c("m11", "m12", "m21", "m22", "y1", "y2"))
plot(p2)
```

# Fewer Variables

The follow code just illustrates how to plot fewer variables:

## 3-$x$-2$y$ Plots

```{r}
p2 <- plot(fit_res_add,
           x_names = c("x1", "m11", "m12"),
           y_names = c("y1", "y2"))
plot(p2)
```

## Use a Named Vector to Change Variable Names in the Plots

```{r}
p2 <- plot(fit_res_add,
           x_names = c(IV1 = "x1", Med1 = "m11", Med2 = "m12"),
           y_names = c(DV1 = "y1", DV2 = "y2"))
plot(p2)
```

# Plot Only One Partial Plot

This example also illustrates how to change the style.

Note that, if `ggplot2` functions are used when changing the
aesthetics, users need to load `ggplot2` first, e.g., `rel()`.

```{r}
library(ggplot2)
p2 <- plot(fit_res_add,
           x_names = "x1",
           y_names = "m11",
           partial_point_aes = list(size = 4,
                                    color = "blue"),
           partial_reg_aes = list(size = 10),
           partial_loess_aes = list(color = "black",
                                    linetype = "dashed"),
           partial_b_aes = list(size = rel(10)))
plot(p2)
```

# Plot of Residuals only

By setting `what = "residual"`, the `plot()` method can
produce only plots for residuals of endogenous variables:

```{r}
p <- plot(fit_res_add,
          what = "residual")
print(p)
```

Users can also use `y_names` to select only some of the
endogenous variables for the plot:

```{r}
p <- plot(fit_res_add,
          what = "residual",
          y_names = c("m11", "m12"))
print(p)
```